---
title: "Yang's Personal Project, Toronto Covid-19 Studies"
author: "Yang Shang, 1002603765"
date: "27/09/2020"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
```

```{r}
library(opendatatoronto)
library(ggplot2)
packages <- show_package("64b54586-6180-4485-83eb-81e8fae3b8fe")
resources <- list_package_resources("64b54586-6180-4485-83eb-81e8fae3b8fe")
covid_resources <- filter(resources, tolower(format) %in% c('csv', 'geojson'))
covid_case_report <- filter(covid_resources, row_number()==1) %>% get_resource()
covid_case_report
```

\quad This data set collects all reported Covid-19 cases in Toronto, On, Canada. Until September $11^{th}$, 2020, 17872 cases were reported. Each case is assigned a unique ID. Patients were labeled by their age groups, area of living (Neighborhood Name), source of infection, episode date, reported date, gender, outcome, and states of treatments.


\quad I would like to first study about the trend of daily reported increasing cases. As "Date" is a discrete variable, I will use a bar graph. The x-axis is the reported date and y-axis is the number of reported cases.

```{r plots}
ggplot(covid_case_report,aes(x=`Reported Date`))+geom_bar(colour="Blue")+
  theme(axis.text.x=element_blank())+
  labs(x="Reported Dates (since 2020-01-23)",y="Number of Cases",
       title="Covid-19, Daily Reported Cases in Toronto",
       subtitle="2020-01-23 to 2020-09-21")
```

\quad As each column represents number of reported cases on a unique day, I am able to see the trend of the pandemic through increase and decrease in daily reported cases. The plot shows a Bi-modal shape, where the first climax was reached around March to May and the second one was reached in September.

\quad By news from Toronto Government, sourced from https://www.toronto.ca/news/city-of-toronto-now-in-stage-3-reopening/, Toronto was reopened from pandemic on July $31^{st}$, 2020. By the bar grouph, the day is approximately the local minimum of dayly reported cases. Since then, the reported cases started to increase again. 
\vspace{10pt}

\quad I also would like to study about the comprehensive response time of individuals and Toronto government towards covid-19. I will approximate the response time by calculating the differences between episode date and reported date.

```{r}
date2 <- data.frame(Episode_Date=c(covid_case_report$`Episode Date`),
                    Reported_Date=c(covid_case_report$`Reported Date`))
date2$date_diff <- as.Date(as.character(date2$Reported_Date),format="%Y-%m-%d")-
  as.Date(as.character(date2$Episode_Date),format="%Y-%m-%d")
```

\quad The mean of estimated response time is

```{r}
mean(date2$date_diff)
```

with variance of

```{r}
var(date2$date_diff)
```

\quad Shown by a density plot, we obtain

```{r plot}
ggplot(date2,aes(x=date_diff,y=..density..))+
  geom_density(colour="Red")+
  geom_vline(xintercept=quantile(date2$date_diff,0.90))+
  labs(x="Estimated Response Time (days)",y="Density",
       title="Estimated Response Time to Covid-19 Cases")
```

\quad The density plot shows that most Covid-19 cases are responded around 5.977171 days, and 90 percent of the cases are responded under 13 days. The generally agreed self-isolation duration is 14 days, where 13 days is within this range. Thus for a person suspect to have infected Covid-19, it is 90% confident to confirm the case within 2 weeks.